---
title: "clean_data"
output: rmarkdown::html_vignette
vignettes: >
  %\VignetteIndexEntry{clean_data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The clean_data function is designed to clean your data by performing two key operations:

+ Removing missing values: The function automatically omits rows containing NA values.
+ Standardizing text: It replaces spaces and slashes in the dataset with periods (".").

This function is useful when preparing raw data for analysis, ensuring that your dataset is free of missing values and uses consistent formatting.

### Data Requirements

The input for this function should be a data frame (df). The data frame should contain any type of data that may require cleaning

## Installation Instructions

To install and load the LanguirandR package, use the following commands:

```{r setup}
devtools::install_github("kaitlinlanguirand/Project_3")
library(LanguirandR)

```


## Example

### Download Data

Before using the clean_data function, you need to download and load your data. Here’s how to get the log_1.
   
```{r}
download.file(
  url = "https://github.com/kaitlinlanguirand/Project_3/raw/refs/heads/main/datasets_project3/log_1.log",
  destfile = "datasets_project3/log_1.log",
  mode = "wb" 
)

log_1 <- read_table("/cloud/project/datasets_project3/log_1.log")

```


### Use Function

Once your data is loaded, you can use the clean_data function to clean it by removing NA values and standardizing text:

```
LanguirandR::clean_data(log_1)
```

### Conclusion

The clean_data function is an efficient tool for cleaning your data frames by removing NA values and standardizing text formatting. This ensures that your data is ready for analysis without the hassle of manual cleaning.
