---
title: "crazy_histogram"
output: rmarkdown::html_vignette
vignettes: >
  %\VignetteIndexEntry{crazy_histogram}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The crazy_histogram function creates a visually unique, jittered histogram where the data points are displayed in various shapes and colors. The function allows you to select a column from your dataset and display it with customized axis titles and a plot title.

This function is ideal when you want to create an aesthetically unconventional histogram with individual data points visible in a scattered fashion.

### Data Requirements

The function requires a data frame (df) with a numeric column that will be plotted. The following parameters are needed:

+ df: The input data frame containing the data to be visualized.
+ column: The name of the column you want to plot (it should be a numeric column).
+ title: The title of the plot.
+ x_title: The label for the x-axis.
+ y_title: The label for the y-axis.


## Installation Instructions

To install and load the LanguirandR package, use the following commands:

```{r setup}
devtools::install_github("kaitlinlanguirand/Project_3")
library(LanguirandR)

```

## Example

You can download sample data and load it into R as shown below:

### Download Data
```{r}
download.file("https://github.com/kaitlinlanguirand/Project_3/raw/refs/heads/main/datasets_project3/log_1.log", "datasets_project3/log_1.log")

log_1 <- read_table("/cloud/project/datasets_project3/log_1.log")

```

### Use Function

Once your data is loaded, you can create a customized jittered histogram using the crazy_histogram function. This function takes in a column from your dataset and generates a plot with unique visual elements.

```{r eval=FALSE, fig.width=8, warning=FALSE, include=FALSE}
LanguirandR::crazy_histogram(log_1, "Posterior", "Posterior Frequency", "Posterior", "Frequency")
```

### Conclusion

The crazy_histogram function is a creative way to visualize data with jittered points, where each data point is presented with different sizes, colors, and shapes. It allows for a dark-themed, artistic display of your data while retaining useful visual insights.
