---
title: "density_plot"
output: rmarkdown::html_vignette
vignettes: >
  %\VignetteIndexEntry{density_plot}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The density_plot function enables users to create a density plot by selecting a column from a chosen data frame. This tool is ideal for visualizing data distributions and includes jittered points for added clarity. It is designed for ease of use, requiring minimal customization beyond selecting your data and titles for the axis. 

### Data Requirements
To use the density_plot function, ensure your input data meets these requirements:

1. Data Frame
The function requires a data frame (df) as input. Your data should be structured in rows and columns, with each column representing a variable.

2. Two Numeric Columns
You need to specify two numeric columns from the data frame. These columns will be plotted on the x- and y-axes respectively:

3. Labels
When calling the function, provide the column names,plot title, x-axis label, and the y-axis label as strings (enclosed in quotation marks) to match the exact names in the data frame.

Its going to be in this order when you are done:
density_plot <- function(df, x_column1, x_column2, plot_title, x_title, y_title)

## Installation Instructions

To install and load the package containing the function, follow these steps:

```{r setup}
devtools::install_github("kaitlinlanguirand/Project_3")
library(LanguirandR)

```


## Example

### Download Data
To demonstrate the function, download example data files from the repository and load them into R:

```{r}
if (!dir.exists("datasets_project3")) {
  dir.create("datasets_project3")
}
download.file(
  url = "https://github.com/kaitlinlanguirand/Project_3/raw/refs/heads/main/datasets_project3/log_1.log",
  destfile = "datasets_project3/log_1.log",
  mode = "wb" 
)
log_1 <- read_table("/cloud/project/datasets_project3/log_1.log")

download.file(
  url = "https://github.com/kaitlinlanguirand/Project_3/raw/refs/heads/main/datasets_project3/log_2.log",
  destfile = "datasets_project3/log_2.log",
  mode = "wb"
)

log_2 <- read_table("/cloud/project/datasets_project3/log_2.log")

```


### Use Function

Here’s how to use the density_plot function with the example dataset:

```{r, fig.cig.cap="Density plot comparing Posterior and Likelihood", alt="A density plot comparing the distribution of 'Posterior' and 'Likelihood' values from the log_1 dataset."}
library(ggplot2)
LanguirandR::density_plot(log_1, "Posterior", "Likelihood", "Posterior and Likelihood Density", "Variables", "Density")
```


### Notes

+ Ensure your data frame contains the specified numeric columns.
+ Customize the column inputs and titles to suit your specific dataset and visualization needs.
+ The function is pre-styled and does not require manual theme adjustments

### Conclusion

The density_plot function simplifies the creation of visually appealing density plots. It is suitable for exploratory data analysis, presentations, and professional reporting. Use the examples provided to start visualizing your data distributions effectively.
