---
title: "rename_variable"
output: rmarkdown::html_vignette
vignettes: >
  %\VignetteIndexEntry{rename_variable}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The rename_variable function allows users to rename a column in a data frame. This is particularly useful when preparing data for analysis, as it enables you to adjust column names to be more descriptive or standardized.

###Data Requirements

1. Data Frame
The input must be a data frame. This can be any data frame that contains the column you wish to rename.

2. Old Column Name
You must provide the current name of the column you want to rename. This should be passed as a string.

3. New Column Name
You must also provide the new name for the column, which should also be a string.

### Installation Instructions
To install and load the LanguirandR package, use the following commands:
```{r setup}
devtools::install_github("kaitlinlanguirand/Project_3")
library(LanguirandR)

```


## Example

### Download Data

Before using the rename_variable function, you'll need to load your data frame. Here's how to download and load the log_1 data:

```{r}
if (!dir.exists("datasets_project3")) {
  dir.create("datasets_project3")
}
download.file(
  url = "https://github.com/kaitlinlanguirand/Project_3/raw/refs/heads/main/datasets_project3/log_1.log",
  destfile = "datasets_project3/log_1.log",
  mode = "wb" # Use "wb" for binary files to avoid corruption
)
log_1 <- read_table("/cloud/project/datasets_project3/log_1.log")
```
 
 
 
### Use Function

Once your data is loaded, you can use the rename_variable function to rename any column in your data frame:

```{r}
LanguirandR::rename_variable(log_1, "alpha_morpho", "Alpha_Morpho")

```


### Output

After running the function, the specified column in the data frame will be renamed. For example, if the original column is called alpha_morpho, it will be renamed to Alpha_Morpho in the returned data frame.

### Conclusion

The rename_variable function is a quick and effective way to rename columns in your data frames. Whether you're cleaning data or making column names more descriptive for analysis, this function streamlines the renaming process.
