---
title: "run_anova"
output: rmarkdown::html_vignette
vignettes: >
  %\VignetteIndexEntry{run_anova}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

The run_anova function is designed to perform a one-sample ANOVA test on a numeric variable to compare its mean against a specified value (default is 0). This function provides the ANOVA summary table, the F-statistic, and p-value, and additionally runs a t-test to compare the mean of the numeric variable against a hypothesized value. 

## Installation Instructions

To use this function, you will first need to install the package and load it into your R environment.

```{r setup}
devtools::install_github("kaitlinlanguirand/Project_3")
library(LanguirandR)

```


## Example

### Download Data
To demonstrate the function, download example data files from the repository and load them into R:

```{r}
if (!dir.exists("datasets_project3")) {
  dir.create("datasets_project3")
}
download.file(
  url = "https://github.com/kaitlinlanguirand/Project_3/raw/refs/heads/main/datasets_project3/log_1.log",
  destfile = "datasets_project3/log_1.log",
  mode = "wb" # Use "wb" for binary files to avoid corruption
)
log_1 <- read_table("/cloud/project/datasets_project3/log_1.log")

```


### Use Function

You can use the run_anova function to test the mean of a numeric column. In the example below, we test the Posterior column of log_1 against a hypothesized mean of 0.

```{r}
LanguirandR::run_anova(log_1, "Posterior", mu = 0) 
```


### Conclusion

The run_anova function provides a simple and efficient way to test if a numeric variable's mean significantly differs from a hypothesized value. It combines ANOVA and t-test results to give a comprehensive statistical summary.

