---
title: "mosasaur_var_calc"
author: "April Wright"
date: "2024-10-8"
output: var_files
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Let's get some Bayes Factors from our posterior traces.
```{r}
library(tidyverse)
library(ggplot2)
```
We start off by reading in our trace:
```{r}
read_delim(file = "/cloud/project/mosasaur/rjMCMCs/timelines_run_1.log")
```
Next, some helper variables. These are the log BF scores that correspond to weak, substantial, and strong BF support.
```{r}
BF <- c(3.2, 10, 100)
p = BF/(1+BF)
```
Next, this takes a bit of doing. We need to know the proportion of the posterior that each model takes up. 
```{r}
library(tidyverse)
big_trace <- rbind(trace[[1]], trace[[2]])
#trace[[3]], trace[[4]])
count <- big_trace  %>% 
     group_by(alpha_morpho) %>% 
     summarize(count = n())
count$count[1]/sum(count)
count$count[2]/sum(count)
```
This proportion is the Bayes Factor. Now, we need to take this number and compare it to a test statistic using the vector of Bayes Factor test statistics (p) above.
On this plot, each model will be a bar. The prior (equal probability) will be in black. The red lines are support (lowest - weak support, the middle - substantial, the top - strong) The green ones are anti-support. Not sure we can see these with how these are calculated.
```{r}
plotTrace(trace = trace,
          vars = c("character_indicator"))[[1]] +
          ylim(0,1) +
          geom_hline(yintercept=0.3, linetype="solid", color = "black") +
          geom_hline(yintercept=p, linetype=c("longdash","dashed","dotted"), color = "red") +
          geom_hline(yintercept=1-p, linetype=c("longdash","dashed","dotted"), color = "green") +
     # modify legend location using ggplot2
     theme(legend.position = c(0.40,0.825))
```
```{r}
plotTrace(trace = trace,
          vars = c("character_indicator"))[[1]] +
          ylim(0,1) +
          geom_hline(yintercept=0.5, linetype="solid", color = "black") +
          geom_hline(yintercept=p, linetype=c("longdash","dashed","dotted"), color = "red") +
          geom_hline(yintercept=1-p, linetype=c("longdash","dashed","dotted"), color = "green") +
     # modify legend location using ggplot2
     theme(legend.position = c(0.40,0.825))
```
Note that for the FBD, we have 3 models. Thus, a flat prior should be at .33.
```{r}
#trace[[1]] <- trace[[1]] %>% 
#  mutate(fbd_indicator = derivedFactor("1" = (fbd_indicator == 1), "2" = (fbd_indicator != 1)))
plotTrace(trace = trace,
          vars = c("fbd_indicator"))[[1]] +
          ylim(0,1) +
          geom_hline(yintercept=0.33, linetype="solid", color = "black") +
          geom_hline(yintercept=p, linetype=c("longdash","dashed","dotted"), color = "red") +
          geom_hline(yintercept=1-p, linetype=c("longdash","dashed","dotted"), color = "red") +
     # modify legend location using ggplot2
     theme(legend.position = c(0.40,0.825))
```
And the clock:
Note that for the FBD, we have 3 models. Thus, a flat prior should be at .33.You'll notice the ACLN was sampled so infrequently it doesn't show.
```{r}
plotTrace(trace = trace,
          vars = c("clock_indicator"))[[1]] +
          ylim(0,1) +
          geom_hline(yintercept=0.33, linetype="solid", color = "black") +
          geom_hline(yintercept=p, linetype=c("longdash","dashed","dotted"), color = "red") +
          geom_hline(yintercept=1-p, linetype=c("longdash","dashed","dotted"), color = "red") +
     # modify legend location using ggplot2
     theme(legend.position = c(0.40,0.825))
```